---
title: "False_Bay_monitoring_tides"
author: "Wendel Raymond"
date: "April 5, 2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
## False Bay Monitoring Tides
Extract and view tides critical for the water quality monitoring project. 

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(rtide)
library(scales)
```


### Get tide data
From April to September 2021
```{r}
## Data extract ##
dat <- rtide::tide_height("Port Townsend", from = as.Date("2022-09-01"), to = as.Date("2022-12-01"), minutes = 10L, tz = "PST8PDT")

## add feet column ##
dat$TideHeight_ft <- dat$TideHeight * 3.281

## Clean up date data ##
dat$DateTime <- as.POSIXct(dat$DateTime, format = "%Y-%m-%d %h:%m:%s", tz = "PST8PDT")

dat <- dat %>% 
  separate(DateTime, c("date", "time"), sep = " ", remove = FALSE)

## Create continuous time ##
dat$time_cont <- seq(0, 132530, by = 10)
```

Quick plot
```{r}
ggplot(dat) +
  geom_line(aes(x = DateTime, y = TideHeight_ft)) +
  scale_x_datetime(breaks = seq(as.POSIXct("2022-10-01 00:00:00"), as.POSIXct("2022-10-21 00:00:00"), "1 day"), limits = c(as.POSIXct("2022-10-01 00:00:00"), as.POSIXct("2022-10-21 00:00:00")), labels = date_format("%d")) +
  geom_hline(aes(yintercept = 3), color = "red") +
  theme_classic()
```

### Filter tide data

Filter for all data when height is <= 3 feet. 
```{r}
dat.redu <- dat %>%
  filter(TideHeight_ft <= 3)

unique(dat.redu$date)

dat.3ft <- dat.redu %>% 
  group_by(date) %>% 
  summarize(start = min(time_cont),
            end = max(time_cont))

ggplot(dat.redu) +
  geom_line(aes(x = DateTime, y = TideHeight_ft)) +
  scale_x_datetime(labels = date_format("%b"))
```

